Figures

### 2019-05-16 manuscript/figures.Rmd
separate cdl and buffer analyses
pull from stream_buffer Rmd

```{r lulc_vs_iws-lulc, fig.cap = "Stream buffer versus IWS lulc.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/buffer-lulc_vs_iws-lulc-1.pdf")
```

>>>>

```{r cdl_viewport, fig.cap = "CDL landuse cover in example IWS.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/cdl_viewport-1.pdf")
```

```{r lulc_vs_iws-lulc, fig.cap = "Stream buffer versus IWS lulc.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/09_stream_buffer-1.pdf")
```
